---
title: "9041 Assignment 2"
author: Marjan Nikbakhtzadeh
date: today
format:
  html:
    toc: true
    code-fold: true
    code-summary: "Show code"
    df-print: paged
execute:
  echo: false
  warning: false
---

```{r setup}
library(tidyverse)
library(psych)
library(readxl)
library(gt)
library(janitor)

# Load and clean data
data <- read_excel("Attachment_Anxiety_Data.xlsx") %>%
  clean_names()

# Convert questionnaire responses to integer
data <- data %>%
  mutate(
    across(
      c(starts_with("sa_"),
        starts_with("aa_"),
        starts_with("s_est_")),
      as.integer
    )
  )

# Label demographic variables
data <- data %>%
  mutate(
    gender = case_when(
      gender == "1" ~ "Male",
      gender == "2" ~ "Female"
    ),
    age_group = case_when(
      age_group == "1" ~ "18-24",
      age_group == "2" ~ "24-34",
      age_group == "3" ~ "35-44",
      age_group == "4" ~ "45-54",
      age_group == "5" ~ "55-64"
    )
  )

# Sample size
sample_size <- nrow(data)

# Answer keys
sa_key <- list(
  Social_Anxiety = c(
    "sa_1", "sa_2", "sa_3", "sa_4", "-sa_5",
    "sa_6", "sa_7", "sa_8", "-sa_9", "sa_10",
    "-sa_11", "sa_12", "sa_13", "sa_14", "sa_15",
    "sa_16", "sa_17", "sa_18", "sa_19", "sa_20"
  )
)

aa_key <- list(
  Attachment_Anxiety = c(
    "aa_1", "aa_2", "aa_3", "aa_4", "aa_5",
    "aa_6", "aa_7", "aa_8", "aa_9"
  )
)

se_key <- list(
  Self_Esteem = c(
    "s_est_1", "-s_est_2", "s_est_3", "s_est_4",
    "-s_est_5", "-s_est_6", "s_est_7", "-s_est_8",
    "-s_est_9", "s_est_10"
  )
)

# Score the three scales
sa_scores <- scoreItems(sa_key, data, min = 0, max = 4)
aa_scores <- scoreItems(aa_key, data, min = 1, max = 7)
se_scores <- scoreItems(se_key, data, min = 1, max = 4)

sa_df <- as.data.frame(sa_scores$scores)
aa_df <- as.data.frame(aa_scores$scores)
se_df <- as.data.frame(se_scores$scores)

scale_scores <- cbind(sa_df, aa_df, se_df)
data_combined <- cbind(data, scale_scores)

# Demographic table
demographic_table <- data_combined %>%
  tabyl(gender, age_group)

demographic_gt <- demographic_table %>%
  gt() %>%
  tab_header(
    title = "Demographic Summary"
  )

# Overall score table
summary <- describe(
  data_combined %>%
    select(Social_Anxiety, Attachment_Anxiety, Self_Esteem)
)

summary_df <- as.data.frame(summary)

summary_df$Scales <- c(
  "Social Anxiety",
  "Attachment Anxiety",
  "Self-Esteem"
)

alpha_table <- data.frame(
  Alpha = c(
    round(sa_scores$alpha[1], 2),
    round(aa_scores$alpha[1], 2),
    round(se_scores$alpha[1], 2)
  )
)

score_table_final <- cbind(
  summary_df %>%
    select(Scales, mean, median, sd, range),
  alpha_table
)

score_gt <- score_table_final %>%
  gt() %>%
  tab_header(
    title = "Scale Summary Statistics"
  ) %>%
  fmt_number(
    columns = c(mean, median, sd, range),
    decimals = 2
  )

# Filter female participants
filtered_data <- data_combined %>%
  filter(gender == "Female")

filtered_summary <- describe(
  filtered_data %>%
    select(Social_Anxiety, Attachment_Anxiety, Self_Esteem)
)

filtered_summary_df <- as.data.frame(filtered_summary)

filtered_summary_df$Scales <- c(
  "Social Anxiety",
  "Attachment Anxiety",
  "Self-Esteem"
)

# Recalculate alpha for female participants
filtered_sa_scores <- scoreItems(
  sa_key, filtered_data, min = 0, max = 4
)

filtered_aa_scores <- scoreItems(
  aa_key, filtered_data, min = 1, max = 7
)

filtered_se_scores <- scoreItems(
  se_key, filtered_data, min = 1, max = 4
)

filtered_alpha_table <- data.frame(
  Alpha = c(
    round(filtered_sa_scores$alpha[1], 2),
    round(filtered_aa_scores$alpha[1], 2),
    round(filtered_se_scores$alpha[1], 2)
  )
)

filtered_score_table_final <- cbind(
  filtered_summary_df %>%
    select(Scales, mean, median, sd, range),
  filtered_alpha_table
)

filtered_score_gt <- filtered_score_table_final %>%
  gt() %>%
  tab_header(
    title = "Scale Summary Statistics – Female Participants"
  ) %>%
  fmt_number(
    columns = c(mean, median, sd, range),
    decimals = 2
  )
```

## Intro

## Methods

### Participants

The sample consisted of `r sample_size` participants.

```{r}
demographic_gt
```

### Measures

The Social Interaction Anxiety Scale (SIAS) was used to measure social interaction anxiety. The scale demonstrated good internal consistency in the present sample, with a Cronbach's alpha of `r round(sa_scores$alpha[1], 2)`.

The Experiences in Close Relationships Anxiety Subscale was used to measure attachment-related anxiety. Its Cronbach's alpha was `r round(aa_scores$alpha[1], 2)`.

The Rosenberg Self-Esteem Scale was used to measure self-esteem. Its Cronbach's alpha was `r round(se_scores$alpha[1], 2)`.

### Data Analysis Strategy

The questionnaire items were scored using the `scoreItems()` function. Reverse keying was applied to the specified items before calculating the scale scores. For the Social Interaction Anxiety Scale, items 5, 9, and 11 were reverse-keyed. For the Rosenberg Self-Esteem Scale, items 2, 5, 6, 8, and 9 were reverse-keyed. No items were reverse-keyed for the Attachment Anxiety scale. Average scores were then calculated for each scale.

## Results

The overall scale scores are presented in the table below.

```{r}
score_gt
```

The mean score for Social Anxiety was `r round(summary_df$mean[1], 2)`, the mean score for Attachment Anxiety was `r round(summary_df$mean[2], 2)`, and the mean score for Self-Esteem was `r round(summary_df$mean[3], 2)`.

The table below presents the scale scores for female participants.

```{r}
filtered_score_gt
```

Among female participants, the mean score for Social Anxiety was `r round(filtered_summary_df$mean[1], 2)`, the mean score for Attachment Anxiety was `r round(filtered_summary_df$mean[2], 2)`, and the mean score for Self-Esteem was `r round(filtered_summary_df$mean[3], 2)`.